Individual and Differential Harm in Redistricting

### 2022-04-05 paper/paper.Rmd
typos

We sample 1,000 districting plans using the SMC algorithm of @mccartan2020, setting constraints to favor compact plans with district boundaries that tend to follow county lines.
One such plan is shown in Figure \ref{fig:nj-maps}(d).
For each of these sampled plans and the two gerrymanders, we calculate the average harm and differential partisan harm,[^2] as well as the expected number of Democratic seats, the efficiency gap, partisan bias, the mean-median score, and partisan declination.
[^3] The distribution of these measures, along with their pairwise relationships, are shown in Figure \ref{fig:nj-pairs}.

@@

```{r nj-pairs, fig.cap="Scatterplots for all pairs of measures. Point lightness indicates the number of Democratic seats won at baseline (ranging from 7 (dark) to 10 (light)). The Democratic and Republican gerrymanders are shown with the blue and red lines and crosses. The dashed line indicates a value of zero. Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```

>>>>

We sample 10,000 districting plans using the SMC algorithm of @mccartan2020, setting constraints to favor compact plans with district boundaries that tend to follow county lines.
One such plan is shown in Figure \ref{fig:nj-maps}(d).
For each of these sampled plans and the two gerrymanders, we calculate the average harm and differential partisan harm,[^2] as well as the expected number of Democratic seats, the efficiency gap, partisan bias, the mean-median score, and partisan declination.
[^3] The distribution of these measures, along with their pairwise relationships, are shown in Figure \ref{fig:nj-pairs}.

@@

```{r nj-pairs, fig.cap="Scatterplots for all pairs of measures. Point lightness indicates the number of Democratic seats won at baseline, ranging from 7 (dark) to 10 (light). The Democratic and Republican gerrymanders are shown with the blue and red lines and crosses. The dashed line indicates a value of zero. Below the diagonal, numbers indicate the absolute value of the correlation between variables.", fig.width=7, fig.height=7}
include_graphics(here("paper/figures/nj_pairs.pdf"))
```
